### Documentation
# This script is called by "model_municipalities.R" to generate its output. This needs to be called by knitr's knit2html function.
# Nothing really happens in this script. It's merely a template for the output.

---
title: "Mexico Municipality Model Output"
output: html_document
---

Variation: `r sub_output_dir`
------

Parameters
--------
- Subset Data Method: `r subsetData_method`
- Variable Removal Method: `r varRemove_method`
- Get Independent Variables Method: `r getIndeps_method`
- Get Dependent Variables Method: `r getDeps_method`
- Get Weights Method: `r getWeights_method`
- Nfold Cross Validation `r nfolds`
- Elastic-Net Alpha: `r alpha`
- Set Seed: `r seed_set`
- Start Time: `r model_start_time`
- End Time: `r model_end_time`
- Time Elapsed: `r difftime(model_end_time, model_start_time, units="mins")`

Diagnostics
------
```{r diagnostics}
odd_municipalities
odd_municipality_deaths_pct
sort(null_vars)
sort(infinite_vars)
sort(string_vars)
list(rows=nrow(data), columns=ncol(data))
complete_cases_pct
sort(names(data))
hist(deaths_dist, breaks=length(deaths_dist))
hist(mmr_dist, breaks=length(mmr_dist))
```

<!--
Linear LASSO
--------
```{r linear_lasso}
plot(lasso.linear)
plot(cv.lasso.linear)
cv.lasso.linear.coef.min[order(-cv.lasso.linear.coef.min),,drop=FALSE]
cv.lasso.linear.coef.1se[order(-cv.lasso.linear.coef.1se),,drop=FALSE]
```
-->

Binomial LASSO
------
```{r binomial_lasso}
plot(lasso.logit)
plot(cv.lasso.logit)
#cv.lasso.logit.coef.min[order(-cv.lasso.logit.coef.min),,drop=FALSE]
cv.lasso.logit.coef.1se[order(-cv.lasso.logit.coef.1se),,drop=FALSE]
```

<!--
Poisson LASSO
------
```{r poisson_lasso}
plot(lasso.poisson, label=TRUE)
plot(cv.lasso.poisson)
cv.lasso.poisson.coef.min[order(-cv.lasso.poisson.coef.min),,drop=FALSE]
cv.lasso.poisson.coef.1se[order(-cv.lasso.poisson.coef.1se),,drop=FALSE]
```
-->

CHAID
------
```{r chaid_anova}
plot(chaid, uniform=TRUE)
text(chaid, cex=.8)
plotcp(chaid)
sort(chaid$variable.importance, decreasing = TRUE)[1:20]
```

<!--
CHAID Poisson
------
```{r chaid_poisson}
plot(chaid.poisson, uniform=TRUE)
text(chaid.poisson, cex=.8)
plotcp(chaid.poisson)
```
-->

Random Forest
------
```{r random_forest}
print(random.forest)
varImpPlot(random.forest)
```

<!--
Linear Model 1se
-----
```{r linear_model_1se}
summary(linear.model.1se)
anova(linear.model.1se, "Chisq")
hist(residuals(linear.model.1se), breaks=nrow(linear.matrix.1se))
summary(residuals(linear.model.1se)^2)
summary(abs(residuals(linear.model.1se)))
plot(residual.tree.linear.1se, uniform=TRUE)
text(residual.tree.linear.1se, use.n=TRUE, all=TRUE, cex=.8)
```

Linear Model min
------
```{r linear_model_min}
summary(linear.model.min)
#anova(linear.model.min, "Chisq")
hist(residuals(linear.model.min), breaks=nrow(linear.matrix.min))
#summary(residuals(linear.model.min)^2)
#summary(abs(residuals(linear.model.min)))
plot(residual.tree.linear.min, uniform=TRUE)
text(residual.tree.linear.min, use.n=TRUE, all=TRUE, cex=.8)
```
-->


Logit Model 1se
-----
```{r logit_model_1se}
summary(logit.model.1se)
anova(logit.model.1se, "Chisq")
hist(residuals(logit.model.1se), breaks=nrow(logit.matrix.1se))
summary(residuals(logit.model.1se)^2)
summary(abs(residuals(logit.model.1se)))
plot(residual.tree.logit.1se, uniform=TRUE)
text(residual.tree.logit.1se, use.n=TRUE, all=TRUE, cex=.8)
```

<!--
Logit Model min
----
```{r logit_model_min}
summary(logit.model.min)
#anova(logit.model.min, "Chisq")
hist(residuals(logit.model.min), breaks=nrow(logit.matrix.min))
#summary(residuals(logit.model.min)^2)
#summary(abs(residuals(logit.model.min)))
plot(residual.tree.logit.min, uniform=TRUE)
text(residual.tree.logit.min, use.n=TRUE, all=TRUE, cex=.8)
```
-->
<!--
Poisson Model 1se
-----
```{r poisson_model_1se}
summary(poisson.model.1se)
#anova(poisson.model.1se, "Chisq")
hist(residuals(poisson.model.1se), breaks=nrow(poisson.matrix.1se))
summary(residuals(poisson.model.1se)^2)
summary(abs(residuals(poisson.model.1se)))
plot(residual.tree.poisson.1se, uniform=TRUE)
text(residual.tree.poisson.1se, use.n=TRUE, all=TRUE, cex=.8)
```

Poisson Model min
-----
```{r poisson_model_min}
summary(poisson.model.min)
#anova(poisson.model.min, "Chisq")
hist(residuals(poisson.model.min), breaks=nrow(poisson.matrix.min))
summary(residuals(poisson.model.min)^2)
summary(abs(residuals(poisson.model.min)))
plot(residual.tree.poisson.min, uniform=TRUE)
text(residual.tree.poisson.min, use.n=TRUE, all=TRUE, cex=.8)
```
-->

<!--
Trees
-----
```{r trees}
summary(residuals(chaid))
summary(abs(residuals(chaid)))
summary(residuals.rf)
summary(abs(residuals.rf))
```
-->

PCA
---
```{r pca}
screeplot(pca, type="lines")
```
